---
title: "Lab 09 - Grading the professor, Pt. 1"
author: "Benjamin Egan"
date: "03/17/25"
output: github_document
---

Here is the link to the assignment page: https://datascience4psych.github.io/DataScience4Psych/lab09.html. This includes the relevant information for the assignment alongside required questions I needed to answer.

```{r load-packages, message=FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(ggplot2)
library(tidymodels)
library(openintro)
library(moments)
```

# Part 1 - Exploratory Data Analysis



```{r score distribution, message = FALSE}

view(evals)

evals %>%
  ggplot(aes(
    x = score
  ))+
  geom_histogram(color = "white")+
  labs(
    x = "Score",
    y = NULL,
    title = "Distribution of Scores",
    subtitle = "Average professor evaluation score: (1) very unsatisfactory - (5) excellent"
  )

skewness(evals$score)
median(evals$score)
mean(evals$score)

```

This distribution appears to be negatively skewed (-.699), with the majority of the scores falling above four (median = 4.3, mean = 4.17)


``` {r rating and beauty relationship, message = FALSE}

attractive_score <- evals %>%
  ggplot(aes(
    x = score,
    y = bty_avg
  ))+
  labs(
    x = "Score",
    y = "Beauty rating",
    title = "Relationship between professor rating and attractiveness",
    subtitle = "Average professor evaluation score: (1) very unsatisfactory - (5) excellent"
  )

attractive_score + geom_smooth(se = FALSE, color = "black", span = 1)

```

Based on this graph, I would say there is a positive relationship between professor ratings and perceived attractiveness.

### Replication with geom_jitter()

I changed the visualization to use geom_point() instead of geom_smooth(), which makes using geom_jitter() understandable.

``` {r updated rating and beauty relationship, message = FALSE}

attractive_score + geom_point() + geom_smooth(se = FALSE, color = "black", span = .5)

attractive_score + geom_jitter(width = .05) + geom_smooth(se = FALSE, color = "black", span = .5)

```

geom_jitter() can be extremely useful in visualizing the relationship between a continuous variable and a discrete variable (i.e. a likert scale). The scatterplot utilizing geom_point() can be visually misleading, as you cannot tell if data overlap.

## Linear Regression with a numerical predictor

*Provide your answer here.*  
Add code chunks as needed.

```{r exercise2_code}
# Add your R code here
```

## Additional Exercises

*Repeat the format above for additional exercises.*

## Hint

For Exercise 12, the `relevel()` function can be helpful!
